### 2023-12-04 manuscript.tex
Simplified wording in concluding sentence of results about alignment figure

To illustrate the utility of this method for generating hypotheses to guide the functional dissection of specific proteins, we next compared two regions with elevated values of fraction\_Q and repeat\_QN but different signals of conservation for each (Fig.~\ref{fig:alignment}A-B). Though the alignments of both regions are enriched in glutamine and asparagine residues (Fig.~\ref{fig:alignment}C,E), the first has significant signals of conservation for both features (Fig.~\ref{fig:alignment}D), whereas the second does not (Fig.~\ref{fig:alignment}F). Notably, the first region is from an orthologous group that contains a sequence from the \textit{D. melanogaster} gene {ewg}, which is a transcription factor. As polyglutamine stretches can modulate the activity of transcription factor activation domains, this observation is consistent with the maintenance of an optimal level of transcriptional activation mediated by constraints on glutamine-associated features~\cite{Mitchell1989, Gerber1994}. In contrast, the low likelihood ratios of the second region, whose \textit{D. melanogaster} gene is unannotated, are suggestive of unconstrained glutamine repeat expansion and contraction. Interestingly, this region has highly significant likelihood ratios for several features associated with glycine or phenylalanine repeats despite having few of these residues. However, careful inspection of the alignment reveals several positions where such repeats appear in only one or two sequences, \textit{e.g.} columns 153 and 208. While these strong signals of conservation may represent artifacts of applying a continuous model of trait evolution to features derived from discrete data, they could also indicate true constraints against the presence of flexible or hydrophobic patches in those sequence segments. Taken together, these result highlight the ability of this method to identify biochemical features with signals of constrained evolution while also emphasizing the importance of combining those results with biochemical intuition to suggest plausible hypotheses.

>>>>

To illustrate the utility of this method for generating hypotheses to guide the functional dissection of specific proteins, we next compared two regions with elevated values of fraction\_Q and repeat\_QN but different signals of conservation for each (Fig.~\ref{fig:alignment}A-B). Though the alignments of both regions are enriched in glutamine and asparagine residues (Fig.~\ref{fig:alignment}C,E), the first has significant signals of conservation for both features (Fig.~\ref{fig:alignment}D), whereas the second does not (Fig.~\ref{fig:alignment}F). Notably, the first region is from an orthologous group that contains a sequence from the \textit{D. melanogaster} gene {ewg}, which is a transcription factor. As polyglutamine stretches can modulate the activity of transcription factor activation domains, this observation is consistent with the maintenance of an optimal level of transcriptional activation mediated by constraints on glutamine-associated features~\cite{Mitchell1989, Gerber1994}. In contrast, the low likelihood ratios of the second region, whose \textit{D. melanogaster} gene is unannotated, are suggestive of unconstrained glutamine repeat expansion and contraction. Interestingly, this region has highly significant likelihood ratios for several features associated with glycine or phenylalanine repeats despite having few of these residues. However, careful inspection of the alignment reveals several positions where such repeats appear in only one or two sequences, \textit{e.g.} columns 153 and 208. While these strong signals of conservation may represent artifacts of applying a continuous model of trait evolution to features derived from discrete data, they could also indicate true constraints against the presence of flexible or hydrophobic patches in those sequence segments. Taken together, these results highlight this method's ability to identify biochemical features with signals of constrained evolution while also emphasizing the importance of combining those results with biochemical intuition to suggest plausible hypotheses.
